Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-30 tex/paper.tex
save

\glnote{We should further discuss that in practice, the equality may never hold.
We should discuss in which circumstances. In such case, the pivotal quantity
constraint can however be enforced by outweighting the $L_r$, resulting in a
trade-off between classifier optimality and pivotality.}

>>>>

\glnote{We should further discuss that in practice, the equality may never hold.
We should discuss in which circumstances. In such case, the pivotal quantity
constraint can however be enforced by outweighting the $L_r$ term, resulting in a
trade-off between classifier optimality and pivotality.}
